Using Deep Learning to Perform Fuzzy Joins

### 2018-05-09 paper/Triplet_loss.tex
next draft of paper

\subsection{Triplet Loss}
While the previos aproach maps 2 entities at a time using 2 networks that share weights, this aproach maps 3 entities at a time with 3 networks: the anchor the positive and the negative. By doing this we can at the same time maximise the distance between two unmatched pairs and minimize the distance between two matched pairs.\cite{schroff2015facenet} We do this by minimizing the following loss function: \[ L(\vec{X}_a, \vec{X}_n, \vec{X}_p) = |\:||\vec{X}_a - \vec{X}_p||^2 - ||\vec{X}_a - \vec{X}_n||^2 + \alpha|\] where \vec{X}_a, \vec{X}_n, \vec{X}_p are the embedded anchor, negative and positive vectors and \alpha is a constant margin. The key choice here is which vectors to include in the training set. If too many easy triplets are including it will slow down the learning since the constraint will be easily satisfied. If too many hard triplets are included the network will learn a strange function based on unusual cases.

>>>>

\subsection{Triplet Loss}
While the previos aproach maps 2 entities at a time using 2 networks that share weights, this aproach maps 3 entities at a time with 3 networks: the anchor the positive and the negative. The loss function minimizes the difference between the anchor and the positive at the same time as it maximises the difference between the anchor and the negative. By doing this we can deal with an unmatched pair and a matched pair at the same time: the anchor is one name, the positive is a match for that name and the negative is another name which is not a match.\cite{schroff2015facenet} We accomplish this by minimizing the following loss function: \[ L(\vec{X}_a, \vec{X}_n, \vec{X}_p) = |\:||\vec{X}_a - \vec{X}_p||^2 - ||\vec{X}_a - \vec{X}_n||^2 + \alpha|\] where $\vec{X}_a$, $\vec{X}_n$, $\vec{X}_p$ are the embedded anchor, negative and positive vectors and $\alpha$ is a constant margin. The key choice here is which vectors to include in the training set. If too many easy triplets are including it will slow down the learning since the constraint will be easily satisfied. If too many hard triplets are included the network will learn a strange function based on unusual cases

### 2018-05-09 paper/introduction.tex
next draft of paper

Our key contributions to the join problem are as follows:
\begin{itemize}
\item We demonstrate that we can use siamese networks to learn a distance function that successfully discriminates same pairs from distance pairs with an F score of .9.  Our results suggest that deep learning models can be used successfully as another mechanism for data driven joins, assuming some sort of filtering approach has been applied to the data.
\item We explore whether it is possible to extend this further, which is to see if the output of the function can in fact be used in an approximate nearest neighbor algorithm to identify neighbors to match with, without any filtering.  
\end{itemize}

>>>>

Our key contributions to the join problem are as follows:
\begin{itemize}
\item We demonstrate that we can use a triplet loss network to learn a distance function that successfully discriminates same pairs from different pairs with an accuracy of 97\%.  Our results suggest that deep learning models can be used successfully as another mechanism for data driven joins, assuming some sort of filtering approach has been applied to the data.
\item We try to extend this further; to see if the output of the function can in fact be used in an approximate nearest neighbor algorithm to identify neighbors to match with, without any filtering. 
\end{itemize}

### 2018-05-09 paper/paper.tex
next draft of paper

\title{Using Machine Learning to Preform Single Column Fuzzy Joins}

@@

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Abraham Judah Gale \\
% \titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Yeshiva University}\\
 %      \affaddr{1932 Wallamaloo Lane}\\
  %     \affaddr{Wallamaloo, New Zealand}\\
       \email{yehuda.gale@gmail.com}
% 2nd. author
\alignauthor
Kavitha Srinivas \\
% \titlenote{The secretary disavows
% any knowledge of this author's actions.}\\
       \affaddr{Rivet Labs}\\
%       \affaddr{P.O. Box 1212}\\
 %      \affaddr{Dublin, Ohio 43017-6221}\\
       \email{Kavitha@rivetlabs.io}
% 3rd. author
\alignauthor Lars Th{\Large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Group}\\
       \affaddr{1 Th{\large{\sf{\o}}}rv{$\ddot{\mbox{a}}$}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\small \texttt{jpkumquat@consortium.net}})}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\begin{abstract}
The abstract for your paper for the PVLDB Journal submission.
The template and the example document are based on the ACM SIG Proceedings  templates. This file is part of a package for preparing the submissions for review. These files are in the camera-ready format, but they do not contain the full copyright note.
Note that after the notification of acceptance, there will be an updated style file for the camera-ready submission containing the copyright note.
\end{abstract}

\include{introduction}
\input{previos_work}
\section{Algorithm}
We started our process with a simple rule based method for matching and another one for blocking.

\subsection{Rule-based Matching}
\begin{table}
\centering
\caption{Table 1}
\begin{tabular}{|c|c|} \hline
Name&Match\\ \hline
Douglas Adams&Douglas Noel Adams\\ \hline
Andreas Capellanus&Andrea Cappellano \\ \hline
John Adams Whipple&John A. Whipple \\
\hline\end{tabular}
\end{table}

\begin{table*}
\centering
\caption{Table 2}
\begin{tabular}{|c|c|} \hline
Bucket Name&Contents\\ \hline
A&\{John A. Whipple\} \\ \hline
Adams&\{Douglas Adams, Douglas Noel Adams, John Adams Whipple\} \\ \hline
Andreas&\{Andreas Capellanus\} \\ \hline
Andrea&\{Andrea Cappellano\} \\ \hline
Cappellano&\{Andrea Cappellano\} \\ \hline
Capellanus&\{Andreas Capellanus\} \\ \hline
Douglas&\{Douglas Adams, Douglas Noel Adams\} \\ \hline
John&\{John Adams Whipple, John A. Whipple\} \\ \hline
Noel&\{Douglas Noel Adams\} \\ \hline
Whipple&\{John Adams Whipple, John A. Whipple\} \\
\hline\end{tabular}
\end{table*}

In the rule-based method, we block based on items that have one word in common. This is the simplest reasonable blocking strategy. Table 2 illustrates what the blocking of the three names from Table 1 would look like. Out of NUMBER1 pairs, NUMBER2 ended up in the same bucket as all their correct matches. NUMBER3 had at least one correct match in the same bucket. To perform the actual matching, we used three simple rules see Table 3:
\begin{enumerate}

@@

\end{enumerate} 
Even using these three rules in combination resulted in too many false negatives. Therefore we decided to treat all matches resulting from any of the three rules as valid. If we treat it as a success if there is a correct match in any of the first three slots, we get an F\textsubscript{1} of FSCORE1. Since the issue is mostly false negatives, and therefore even some of the first three slots were often empty, so even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.
\input{drlim}
\input{Aproximate_Nearest_Neighbors}
\input{Triplet_loss}
\section{Experiments}
\input{siamese_exper}
\section{Conclusions}
%\end{document}  % This is where a 'short' article might terminate

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}

@@

\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.

@@

\begin{appendix}

\end{appendix}

>>>>

\title{Using Deep Learning to Perform Fuzzy Joins}

@@

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor Abraham Judah Gale \\
% \titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Thesis Submitted to}\\
       \affaddr{Yeshiva University}\\
  %     \affaddr{Wallamaloo, New Zealand}\\
       \email{yehuda.gale@gmail.com}
% 2nd. author
\alignauthor
Kavitha Srinivas \\
% \titlenote{The secretary disavows
% any knowledge of this author's actions.}\\
     \affaddr{Advisor}\\
       \affaddr{Rivet Labs}\\
 %      \affaddr{Dublin, Ohio 43017-6221}\\
       \email{Kavitha@rivetlabs.io}
% 3rd. author
\alignauthor Judah Diament\\
       \affaddr{Advisor}\\
       \affaddr{Yeshiva University }\\
       \email{diament@yu.edu}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% \additionalauthors{Additional authors: John Smith (The Th{\o}rv\"{a}ld Group,
% email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
% (The Kumquat Consortium, email: {\small \texttt{jpkumquat@consortium.net}})}
% \date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\input{introduction}
\input{previos_work}
\section{Algorithm}
\subsection{Rule Based}
We started our process with a simple rule based method for matching and another one for blocking.

\begin{table*}
\centering
\caption{Table 2}
\begin{tabular}{|c|c|} \hline
Bucket Name&Contents\\ \hline
A&\{John A. Whipple\} \\ \hline
Adams&\{Douglas Adams, Douglas Noel Adams, John Adams Whipple\} \\ \hline
Andreas&\{Andreas Capellanus\} \\ \hline
Andrea&\{Andrea Cappellano\} \\ \hline
Cappellano&\{Andrea Cappellano\} \\ \hline
Capellanus&\{Andreas Capellanus\} \\ \hline
Douglas&\{Douglas Adams, Douglas Noel Adams\} \\ \hline
John&\{John Adams Whipple, John A. Whipple\} \\ \hline
Noel&\{Douglas Noel Adams\} \\ \hline
Whipple&\{John Adams Whipple, John A. Whipple\} \\
\hline
\label{word_table}
\end{tabular}
\end{table*}

In the rule-based method, we block based on items that have one word in common. This is the simplest reasonable blocking strategy. Table \ref{word_table} illustrates what the blocking of the three names from Figure \ref{table-example} would look like. To perform the actual matching, we used three simple rules see Table 3:
\begin{enumerate}

@@

\end{enumerate} 
Even using these three rules in combination resulted in too many false negatives. Therefore we decided to treat all matches resulting from any of the three rules as valid.
\input{drlim}
\input{Aproximate_Nearest_Neighbors}
\input{Triplet_loss}
\input{LSTM}
\section{Experiments}
\subsection{Rule Based}
If we treat it as a success if there is a correct match in any of the first three slots, we get an F\textsubscript{1} score of 0.7. Since the issue is mostly false negatives, and therefore even some of the first three slots were often empty, so even if we accept any of the top 1000 as a success, we get FSCORE2, not much better.
\input{siamese_exper}
\section{Conclusions}
While we have a very good machine learning based matcher, that does not appear to translate into very good blocking. We still need to explore why we only getting around 69\% of the matches in the top 40 items, when we have the positive closer than the negative in 97\% of cases.  
%\end{document}  % This is where a 'short' article might terminate

@@

%ACKNOWLEDGMENTS are optional

@@

@@

### 2018-05-09 paper/siamese_exper.tex
next draft of paper

\subsection{Siamese Network}
Our first experiment was using a Siamese network to match already blocked entities. The architecture of the network was as shown in Figure \ref{siamese}. As described above this involves two networks that share weights mapping the inputs onto a vector space and computing distance. Before feeding the entities into the networks, we used Kazuma character embeddings to encode each entity as a vector. We used character level embeddings since many names would not have been represented at all if we had used word level embeddings. We then trained the network on our 182772 pairs of names pulled from DBpedia. These are the pairs we have after running the data through the cleanser. We used 95\% of them for training and withheld 5\% for testing. In addition to these pairs we created an equal number of negative pairs to train the model. Wherever possible, the negative pairs had at least one word in common with each other. This was done so that the model would not just learn the obvious function of reject unrelated pairs. We trained the model in 10 epochs. We found that the fscore on the training data was FSCORE3 and FSCORE4 on the test data. This showed that this architecture is an effective matcher. However we only successfully included the correct match in around 15\% of pairs in the top five. This was barley better than the 5\% we got from the embedding alone. This shows that the Siamese network was an infective blocker
\subsection{Triplet Loss}
The triplet loss experiment was extremely similar to the Siamese one, only we used the Triplet loss network instead of the Siamese one. We used a margin of 1. We also used an LSTM instead of a regular deep neural network to capture more meaning. The last change we used was in selection of negative points, instead of picking them based on some rule, we picked the closest 40 points that were not matches from the character embedding, when we did this we got 69\% of the items in the top 40. This is a relatively effective blocker. It also correctly placed 97\% of positives closer to the anchor than negatives, making it a very effective matcher.

>>>>

\subsection{Siamese Network}
Our first experiment was using a Siamese network to match already blocked entities. The architecture of the network was as shown in Figure \ref{siamese}. As described above this involves two networks that share weights mapping the inputs onto a vector space and computing distance. Before feeding the entities into the networks, we used Kazuma character embeddings to encode each entity as a vector. We used character level embeddings since many names would not have been represented at all if we had used word level embeddings. We then trained the network on our 182772 pairs of names pulled from DBpedia. These are the pairs we have after running the data through the cleanser. We used 95\% of them for training and withheld 5\% for testing. In addition to these pairs we created an equal number of negative pairs to train the model. Wherever possible, the negative pairs had at least one word in common with each other. This was done so that the model would not just learn the obvious function of reject unrelated pairs. We trained the model in 10 epochs. We found that the fscore on the training data was .89 on the test data. This showed that this architecture is an effective matcher. However we only successfully included the correct match in around 15\% of pairs in the top five. This was barely better than the 5\% we got from the embedding alone.
\subsection{Triplet Loss}
The triplet loss experiment was extremely similar to the Siamese one, only we used the Triplet loss network instead of the Siamese one. We used a margin of 1. We also used a GRU instead of a regular deep neural network to capture the order of the words. The last change we used was in selection of negative points, instead of picking them based on some rule, we picked the closest 40 points that were not matches from the character embedding. We did this since those names are the hardest ones for the model to learn, this also avoids the problem in Figure \ref{comp_dif_fail}. When we did this we got 69\% of the items in the top 40. This is a relatively effective blocker. It also correctly placed 97\% of positives closer to the anchor than negatives, making it a very effective matcher.
